Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-02 02_Paper/paper.tex
tex discussion commands.
paper update.

\usepackage[bookmarks=false]{hyperref}
    \hypersetup{colorlinks,
      linkcolor=blue,
      citecolor=blue,
      urlcolor=blue}

@@

% a)	Products’ quality must always be guaranteed.
% b)	In certain cases (especially in series assembly production) there is a delay between quality inspection and end of the production process  high potential for producing scrap 
% c)	By doing quality inspection based on samples, there is still a risk of sending NOK parts to customers
% d)	Cost of quality check might be expensive
% e)	Quality assurance is normally done at the end of production (for assembly processes)   
% f)	Early prediction of the production’s quality  would help to decrease the amount of scrap  and the risk of sending NOK parts to customers
% g)	Variable predictions by using machine learning models is currently widely used in diverse fields due to its accurate predictions  with the data collected from the machines, prediction models can be implemented for specific predicted values

@@

% a)	How quality check is done in production
%        i)	Concepts and sampling plan
%        ii)	Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]

@@

% Predictive analytics as concepts
% Implementation in production
%   - Predictive Maintenance
%   - Scheduling
%   - Other

% If happens to be something with P.A. Quality Check
% b)	Predictive analytics in production focusing in QA
%        i)	Existing approaches and methods

% Note: Ideal is to find a gap in literature, that proves why do we do it and why it is important

@@

% What is the demozelle and why it is relevant as study case
% a)	Description of the assemble process in the Demozelle 
% Incl pictures

\section{Methods} %3/4 Page

% b)	Data  is collected from the demonstration cell and analyzed 
% c)	ML model [regression] is trained [type of model tbd]
\subsection{Measurement}

@@

\subsection{Classifier optimization and testing}

\begin{table}
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100\%
       \end{tabular}
       \caption{Method comparison for fault detection using the industry demo data test set.}
\end{table}

@@

% h)	Explain experiences by doing the research

>>>>

\usepackage[bookmarks=false]{hyperref}
    \hypersetup{colorlinks,
      linkcolor=blue,
      citecolor=blue,
      urlcolor=blue}
\usepackage{xcolor}
\newcommand{\AP}[1]{{\color{blue} {\bf (AP: #1)}}}
\newcommand{\LS}[1]{{\color{purple} {\bf (LS: #1)}}}
\newcommand{\MW}[1]{{\color{teal} {\bf (MW: #1)}}}
\newcommand{\JG}[1]{{\color{green} {\bf (JG: #1)}}}
\newcommand{\DSL}[1]{{\color{blue} {\bf (DSL: #1)}}}

@@

\AP{\begin{itemize}
       \item	Products’ quality must always be guaranteed.
       \item	In certain cases (especially in series assembly production) there is a delay between quality inspection
              and end of the production process high potential for producing scrap 
       \item	By doing quality inspection based on samples, there is still a risk of sending NOK parts to customers
       \item	The cost of quality checks might be expensive
       \item	Quality assurance is normally done at the end of production (for assembly processes)   
       \item	Early prediction of the production’s quality  would help to decrease the amount of scrap  and the risk of sending NOK parts to customers
       \item	Variable predictions by using machine learning models is currently widely used in diverse fields due to its accurate predictions with the data collected from the machines, 
              prediction models can be implemented for specific predicted values
\end{itemize}}

@@

\AP{
\begin{itemize}
\item How quality check is done in production
\item Concepts and sampling plan
\item Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]
\end{itemize}}

@@

\AP{
Predictive analytics as concepts. Implementation in production
\begin{itemize}
       \item Predictive Maintenance
       \item Scheduling
       \item Other
\end{itemize}       
If happens to be something with P.A. Quality Check
\begin{itemize}
       \item	Predictive analytics in production focusing in QA
       \item	Existing approaches and methods
\end{itemize}      
Note: Ideal is to find a gap in literature, that proves why do we do it and why it is important
}

@@

\AP{
What is the demozelle and why it is relevant as study case
Description of the assemble process in the Demozelle 
Incl pictures
}
\section{Methods} %3/4 Page

Data  is collected from the demonstration cell and analyzed

\subsection{Measurement}

@@

\subsection{Classifier optimization and testing}
We work with a total of 462 measurements. 
\begin{table}
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100\%
       \end{tabular}
       \caption{Method comparison for fault detection using the industry demo data test set.}
\end{table}

@@

\AP{explain experiences by doing the research}
